Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-09 edubots_surveys.Rnw
Addressed   P24: "using safer alternatives": This expression is unclear. On the other hand, it is unclear what you were aiming to find out through this option.

Technology or Engineering that started using safer alternatives are less than

>>>>

Technology or Engineering that started using safer alternatives \footnote{This addresses the issue of insecure/unsafe applications which do not cipher messages or can be easily compromised exposing information} are less than
